On proving things

### 2015-10-16 reasoning/huiswerk/inl1019.tex
finsihed 2a, yes all the texts

\section{Positivity and negativity}
\subsection{Prove C keeps occuring in premise and conclusion}
To prove that if formula $C$ occurs positively in one of the premises of a rule,
then the same formula occurs positively in the conclusion fro all rules of GKC

This will be done on a rule by rule basis.
\subsubsection{$R\wedge$}
Suppose C occurs positively in one of the premisses
($\Gamma \Rightarrow A, \Delta$) or ($\Gamma \Rightarrow B,\Delta$),
say in the first one. Thus it occurs positively in a formula in $\Delta$ or
$A$ or negatively in a formula in $\Gamma$. In the first and the last case,
the same holds for the conclusion ($\Gamma \Rightarrow A \wedge B, \Delta)$.
In case C occurs positively in $A$ then by definition it occurs positively
in $A \wedge B$ (even in the case that $C = A$). Hence it occurs positively
in ($\Gamma \Rightarrow A \wedge B, \Delta$). This is what had to be shown.

\end{document}

>>>>

\section{Positivity and negativity}
\subsection{Prove C keeps occuring in premise and conclusion}
To prove that if formula $C$ occurs positively in one of the premises of a rule,
then the same formula occurs positively in the conclusion for all rules of GKC

This will be done on a rule by rule basis.

\subsubsection{$R\wedge$}
Suppose C occurs positively in one of the premisses
($\Gamma \Rightarrow A, \Delta$) or ($\Gamma \Rightarrow B,\Delta$),
say in the first one. Thus it occurs positively in a formula in $\Delta$ or
$A$ or negatively in a formula in $\Gamma$. In the first and the last case,
the same holds for the conclusion ($\Gamma \Rightarrow A \wedge B, \Delta$).
In case C occurs positively in $A$ then by definition it occurs positively
in $A \wedge B$ (even in the case that $C = A$). Hence it occurs positively
in ($\Gamma \Rightarrow A \wedge B, \Delta$). This is what had to be shown.

\subsubsection{$L\vee$}
Suppose C occurs positively in one of the premisses
($\Gamma, A \Rightarrow \Delta$) or ($\Gamma, B \Rightarrow \Delta$),
say in the first one. Thus it occurs positively in a formula in $\Delta$ or 
negatively in a formula in $\Gamma$ or $A$. In the first and the last case,
the same holds for the conclusion ($\Gamma, A \vee B \Rightarrow \Delta$).
In case C occurs negatively in $A$ then by definition it occurs negatively
in $A \vee B$ (even in the case that $C = A$). Hence it occurs negatively
in ($\Gamma, A \vee B \Rightarrow \Delta$). This is what had to be shown.

\subsubsection{$L\to$}
Suppose C occurs positively in one of the premisses
($\Gamma \Rightarrow A, \Delta$) or ($\Gamma, B \Rightarrow \Delta$),
say in the first one. Thus it occurs positively in a formula in $\Delta$ or
$A$ or negatively in a formula in $\Gamma$. In the first and the last case,
the same holds for the conclusion ($\Gamma A \to B \Rightarrow \Delta$).
In case C occurs positively in $A$ then by definition it occurs positively
in $A \to B$ (even in the case that $C = A$). Hence it occurs positively
in ($\Gamma A \to B \Rightarrow \Delta$). This is what had to be shown.

\subsubsection{$L\wedge$}
Suppose C occurs positively the premiss
($\Gamma, A, B \Rightarrow \Delta$). Thus it occurs positively in a formula
in $\Delta$ or negatively in a formula in $\Gamma$, $A$ or $B$.`
In the first and the last case,
the same holds for the conclusion ($\Gamma, A \wedge B \Rightarrow \Delta$).
In case C occurs negatively in $A$ then by definition it occurs negatively
in $A \wedge B$ (even in the case that $C = A$). Hence it occurs negatively
in ($\Gamma, A \wedge B \Rightarrow \Delta$). This is what had to be shown.

\subsubsection{$R\vee$}
Suppose C occurs positively the premiss
($\Gamma \Rightarrow A, B, \Delta$). Thus it occurs positively in a formula
in $\Delta$, $A$ or $B$ or negatively in a formula in $\Gamma$.
In the first and the last case,
the same holds for the conclusion ($\Gamma \Rightarrow A \vee B, \Delta$).
In case C occurs positively in $A$ then by definition it occurs positively
in $A \vee B$ (even in the case that $C = A$). Hence it occurs positively
in ($\Gamma, A \wedge B \Rightarrow \Delta$). This is what had to be shown.

\subsubsection{$R\to$}
Suppose C occurs positively the premiss
($\Gamma, A \Rightarrow B, \Delta$). Thus it occurs positively in a formula
in $\Delta$ or $B$ or negatively in a formula in $\Gamma$ or $A$.
In the first and the last case,
the same holds for the conclusion ($\Gamma \Rightarrow A \to B, \Delta$).
In case C occurs negatively in $A$ then by definition it occurs negatively
in $A \to B$ (even in the case that $C = A$). Hence it occurs negatively
in ($\Gamma, A \to B \Rightarrow \Delta$). This is what had to be shown.

\subsubsection{$L\neg$}
Suppose C occurs positively the premiss
($\Gamma \Rightarrow A, \Delta$). Thus it occurs positively in a formula
in $\Delta$ or $A$ or negatively in a formula in $\Gamma$.
In the first and the last case,
the same holds for the conclusion ($\Gamma, \neg A \Rightarrow \Delta$).
In case C occurs positively in $A$ then by definition it occurs positively
in $\neg A$ (even in the case that $C = A$). Hence it occurs positively
in ($\Gamma, \neg A \Rightarrow \Delta$). This is what had to be shown.

\subsubsection{$R\neg$}
Suppose C occurs positively the premiss
($\Gamma, A \Rightarrow \Delta$). Thus it occurs positively in a formula
in $\Delta$ or negatively in a formula in $\Gamma$ or $A$.
In the first and the last case,
the same holds for the conclusion ($\Gamma \Rightarrow \neg A, \Delta$).
In case C occurs negatively in $A$ then by definition it occurs negatively
in $\neg A$ (even in the case that $C = A$). Hence it occurs negatively
in ($\Gamma \Rightarrow \neg A, \Delta$). This is what had to be shown.
\subsection{Proof introduction of $A\wedge B$ remains positive}
\end{document}
